### 2015-07-11 narrative/naming-service.tex
first bunch of changes in data description.

\subsection{Naming and Discovery Service}
\label{sec:naming-discovery}
\paragraph{Background:}
Given the well documented difficulties with POSIX-compliant naming and our
approach that decomposes what would be a single file into potentially large
number of objects, we must take a new approach to naming.  Data migration, as a
result of system pressures or user/system policies, further adds to the
complexity of managing naming and discovery. Our naming service must maintain
sufficient metadata information, track or be able to find objects as they move
across storage layers, and facilitates data discovery. Since we need to also
support access through POSIX APIs for existing application and system
integration, we must address how to bridge the drastic differences between the
decomposed objects of potentially varying fidelity with potentially multiple
versions with a POSIX API-compatible interface.

@@

The overriding theme for this proposal of providing a cooperative relationship
between the user and the storage system extends into this area as well.
Negotiating the data quality/retrieval time trade-off requires additional
metadata.  Providing this functionality requires the naming service be able to
both return a list of data versions and an indication of data quality. This
will be combined with a retrieval time estimate for each version by the
middleware to determine what data version should be retrieved.  This estimate
will be discussed elsewhere in this proposal.

In addition to the basic naming and data tracking operations, we will also need
to incorporate authorization capabilities. Sirocco currently integrates with a
Kerberos service for authentication. Given a capability ticket, a user can
access different objects as needed. This ticket structure offers protection
services typically offered on POSIX directories and files, but can do it at the
fork level instead. This allows a reduced quality data version to be available
for the general users while the high-quality version would be limited to the
data creator. This and other considerations for security must be incorporated
into the entire naming and metadata service.

>>>>

\subsection{Naming and Discovery Service}
\label{sec:naming-discovery}
\paragraph{Background:}
Given the well documented difficulties with POSIX-compliant naming and our
approach that decomposes what would be a single file into potentially large
number of objects, we must take a new approach to naming.  Data migration, as a
result of system pressures or user/system policies, further adds to the
complexity of managing naming and discovery. Our naming service must maintain
sufficient metadata information, track or be able to find objects as they move
across storage layers, and facilitates data discovery. Since we need to also
support access through POSIX APIs for existing application and system
integration, we must address how to bridge the drastic differences between the
decomposed objects of potentially varying fidelity
with a POSIX API-compatible interface.

@@

The overriding theme for this proposal of providing a cooperative relationship
between the user and the storage system extends into this area as well.
Negotiating the data quality/retrieval time trade-off requires additional
metadata.  Providing this functionality requires the naming service be able to
both return a list of data chunks and an indication of data quality. This
will be combined with a retrieval time estimate by the
middleware/application to determine what data chunks should be retrieved.  This estimate
will be discussed elsewhere in this proposal.

In addition to the basic naming and data tracking operations, we will also need
to incorporate authorization capabilities. Sirocco currently integrates with a
Kerberos service for authentication. Given a capability ticket, a user can
access different objects as needed. This ticket structure offers protection
services typically offered on POSIX directories and files, but can do it at the
fork level instead. This allows a reduced quality data chunk to be available
for the general users while the high-quality data would be limited to the
data creator. This and other considerations for security must be incorporated
into the entire naming and metadata service.
